---
title: "Order statistics"
author: 
  - [add  your name]  
  - [add name of other group members]
date: "Week 2, Math 563, Sp21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,comment = '', fig.width = 3, fig.height = 3
  )
```


--- 

# Background 

> What is the purpose of this worksheet? 

1. Learn using basic R, practice  using Markdown;
2. Create simulations for order statistics.

For more info, formatting, and technical background, see previous handout (on sampling distributions). 

### Installing and loading packages

Just like every other programming language you may be familiar with, R's capabilities can be greatly extended by installing additional "packages" and "libraries".

To **install** a package, use the `install.packages()` command.  You'll want to run the following commands to get the necessary packages for today's lab:

```
install.packages("ggplot2")
```

You only need to install packages once.  Once they're installed, you may use them by **loading** the libraries using the `library()` command.  For today's lab, you'll want to run the following code

```{r}
library(ggplot2) # graphics library
```

# Problem 1: $N(0,1)$

* Let  us pick sample size $n=10$. Let $X\sim N(0,1)$. 
* Repeat  the following  $10,000$  times: 
  * Draw a random sample $X_1,\dots,X_n$ from the  normal  density $f(x)$.  
  * For $k\in\{1,3,5,9,10\}$, compute the $k$-th statistic $y_k$.  
* Plot the histogram of  $y_k$ for each $k$. 

```{r}
# your  code here
```

> Discuss. What do  you  see? 


# Problem 2: $Gamma(1.5,5)$

* Let  us pick sample size $n=25$. Let $X\sim Gamma(1.5,5)$. 
* Repeat  the following  $10,000$  times: 
  * Draw a random sample $X_1,\dots,X_n$ from the  normal  density $f(x)$.  
  * For $k\in\{2,4,16,24\}$ compute the $k$-th statistic $y_k$.  
* Plot the histogram of  $y_k$ for each $k$. 

```{r}
# your  code here
```


> Discuss. What do  you  see? 


# License

This document  is created for Math 563, Spring 2021, at Illinois Tech, taught by Sonja Petrovic^[Sonja Petrović,  Associate Professor of Applied  Mathematics, College of Computing, Illinios Tech.  [Homepage](https://www.SonjaPetrovicStats.com), [Email](mailto:sonja.petrovic@iit.edu).] 

While the course materials are generally not  to be distributed outside the course without permission of the instructor,  this particular set of notes is licensed under a [Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License](https://creativecommons.org/licenses/by-nc-sa/4.0/).


[![Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License][image]][hyperlink]

  [hyperlink]: https://creativecommons.org/licenses/by-nc-sa/4.0/
  [image]: https://i.creativecommons.org/l/by-nc-sa/4.0/88x31.png
    


